### 2018-09-24 paper/complexity.tex
Show that CSP process exists with minHit(P) = n choose floor(n\2)

% -------------------------------------------------------------------------
\subsection{Estimation of $h$}
Given a set $\minaccs(P/s) = \{ A_1,\dots, A_\alpha \}$ of   minimal
acceptances, the cardinality   $h = \minhits(P/s)$ has the upper bound
\[
h \le \binom{n}{\lfloor\frac{n}{2}\rfloor}, \quad \text{where $n = \card{\Sigma}$.}
\]
This follows from Theorem~\ref{th:sperner} and the fact that $\minhits(P/s)$ is a 
Sperner Family, as introduced in Section~\ref{sec:hit}. The next theorem shows that this
upper bound can really be reached by collections of minimal hitting sets.

\begin{theorem}
\label{th:upperboundh}
Let $n\ge 2$ be any positive integer and $\Sigma$  any finite set of cardinality $n$.
Let $C\subseteq 2^\Sigma$ be any collection of  subsets of $\Sigma$. Then  
\[
\text{max}\{\card{\text{minHit}(C)}~|~C\subseteq 2^\Sigma\}=\binom{n}{\lfloor\frac{n}{2}\rfloor}
\]
\end{theorem}
\begin{proof}
For any subset  $B$  of $\Sigma$, define  $A_{B}:=\Sigma\setminus B$.
Define 
$$
C=\{A_{B}~|~ B\subseteq \Sigma, \card{B} < \lfloor\frac{n}{2}\rfloor\}.
$$
Let $H$ be any minimal Hitting set of $C$. Then $H$ contains at least $\lfloor\frac{n}{2}\rfloor$ elements, because 
otherwise there existed an $A_{H}\in C$ with $A_H\cap H=\varnothing$. 
Since $\card{A_{B}}=n-\card{B}>n-\lfloor\frac{n}{2}\rfloor$, for any $B\subseteq \Sigma$ with $\card{B}< \lfloor\frac{n}{2}\rfloor$, we conclude that
 any  subset of $\Sigma$  with at least $\lfloor\frac{n}{2}\rfloor$ elements 
 has a non-empty intersection with all  $A_B\in C$.  
 The number of subsets in $\Sigma$ with exactly $\lfloor \frac{n}{2}\rfloor$ elements
 is $\binom{n}{\lfloor\frac{n}{2}\rfloor}$.
Thus $\card{\text{minHit}(C)} \ge \binom{n}{\lfloor\frac{n}{2}\rfloor}$, and 
Theorem~\ref{th:sperner} yields $\card{\text{minHit}(C)} = \binom{n}{\lfloor\frac{n}{2}\rfloor}$.
\xbox
\end{proof}

>>>>

% -------------------------------------------------------------------------
\subsection{Estimation of $h$}
Given a set $\minaccs(P/s) = \{ A_1,\dots, A_\alpha \}$ of   minimal
acceptances, the cardinality   $h = \minhits(P/s)$ has the upper bound
\[
h \le \binom{n}{\lfloor\frac{n}{2}\rfloor}, \quad \text{where $n = \card{\Sigma}$.}
\]
This follows from Theorem~\ref{th:sperner}, since $\minhits(P/s)$ is a 
Sperner Family, as introduced in Section~\ref{sec:sperner}. 
The next theorem shows that this
upper bound can really be reached by collections of minimal hitting sets associated with 
a CSP process state.

\begin{theorem}
\label{th:upperboundh}
Let  $\Sigma$  be an alphabet with cardinality $n\ge 2$.  Then  
there exists a CSP process $P$ with 
\[
\card{\text{minHit}(P)} = \binom{n}{\lfloor\frac{n}{2}\rfloor}.
\]
\end{theorem}
\begin{proof}
Let $C$ be the collection of all subsets of $\Sigma$ with cardinality 
$n-\lfloor{\frac{n}{2}}\rfloor+1$. Then any CSP process of the form 
\[
P = \Intchoice_{A\in C} e:A\then P(e)
\]
fulfils $\minaccs(P) = C$.
Let $H$ be any minimal Hitting set of $C$. Then $H$ contains at least $\lfloor{\frac{n}{2}}\rfloor$ elements, because 
otherwise
$\card{\Sigma\setminus H} > n-\lfloor{\frac{n}{2}}\rfloor$, 
and any subset $A\subseteq \Sigma\setminus H$ with cardinality
$n-\lfloor{\frac{n}{2}}\rfloor+1$  would be contained in $C$, but satisfy 
$A\cap H=\varnothing$. 
Since $\lfloor{\frac{n}{2}}\rfloor+n-\lfloor{\frac{n}{2}}\rfloor+1=n+1$, we conclude
 that any $\lfloor{\frac{n}{2}}\rfloor$-element subset of $\Sigma$ 
 intersects  every element of $C$.  Therefore, every minimal hitting set of $C$ has exactly $\lfloor{\frac{n}{2}}\rfloor$ elements,
so $\card{\minhits(C)} = \binom{n}{\lfloor{\frac{n}{2}}\rfloor}$.
\xbox
\end{proof}

### 2018-09-24 paper/preliminaries.tex
Show that CSP process exists with minHit(P) = n choose floor(n\2)

The main idea of the underlying test strategy for failures refinement can be
based on solving a \emph{hitting set problem}. Given a finite collection of
finite sets $C = \{ A_1,\dots,A_n\}$, such that each $A_i$ is a subset of a
universe $\Sigma$, a \emph{hitting set} $H\subseteq\Sigma$ is a set
satisfying the following property.
%
\begin{equation}
  \label{eq:hit}
  \forall A\in C: H\cap A \neq\varnothing.
\end{equation}
%
A \emph{minimal hitting set} is a hitting set that cannot be further reduced
without losing the characteristic property (\ref{eq:hit}). By $\minhits(C)$
we denote the collection of minimal hitting sets for a collection $C$. For
the pathological case where $C$ contains an empty set, $\minhits(C)$ is also
empty.

@@

The following lemma establishes that the $conf$ relation specified in
(\ref{eq:conf}) can be characterised by means of minimal acceptances and
their minimal hitting sets.
%
\begin{lemma}
\label{lemma:hseta}
Let $P, Q$ be two finite-state CSP processes.
%% satisfying $P\lessdet_T Q$.
For each $s\in\trc(P)$,
let $\minhits(P/s)$ denote the
collection of all minimal hitting sets of $\minaccs(P/s)$.
Then the following statements are equivalent.
\begin{enumerate}
\item $Q\ conf\ P$

@@

Since minimal acceptances can be used to label the nodes of a normalised transition graph, and since $\minaccs(P/s) = \minaccs(G(P)/s)$, the notation of minimal hitting sets also
carries over to graphs: we write $\minhits(n)$ for nodes $n$ of $G(P)$ and observe that
\begin{equation}
\label{eq:minhitsGP}
\minhits(G(P)/s) = \minhits(P/s) \ \text{for all}\ s\in \trc(P).
\end{equation}

>>>>

\subsubsection*{Definition}
The main idea of the underlying test strategy for failures refinement can be
based on solving a \emph{hitting set problem}. Given a finite collection of
finite sets $C = \{ A_1,\dots,A_n\}$, such that each $A_i$ is a subset of a
universe $\Sigma$, a \emph{hitting set} $H\subseteq\Sigma$ is a set
satisfying the following property.
%
\begin{equation}
  \label{eq:hit}
  \forall A\in C: H\cap A \neq\varnothing.
\end{equation}
%
A \emph{minimal hitting set} is a hitting set that cannot be further reduced
without losing the characteristic property (\ref{eq:hit}). By $\minhits(C)$
we denote the collection of minimal hitting sets for a collection $C$. For
the pathological case where $C$ contains an empty set, $\minhits(C)$ is also
empty.

@@

% ------------------------------------------------------------------------
\subsubsection*{Characterisation of $conf$ by Minimal Hitting Sets}
The following lemma establishes that the $conf$ relation specified in
(\ref{eq:conf}) can be characterised by means of minimal acceptances and
their minimal hitting sets.
%
\begin{lemma}
\label{lemma:hseta}
Let $P, Q$ be two finite-state CSP processes.
%% satisfying $P\lessdet_T Q$.
For each $s\in\trc(P)$,
let $\minhits(P/s)$ denote the
collection of all minimal hitting sets of $\minaccs(P/s)$.
Then the following statements are equivalent.
\begin{enumerate}
\item $Q\ conf\ P$

@@

% -------------------------------------------------------------------------
\subsubsection*{Minimal Hitting Sets of Normalised Transition Graphs}
Since minimal acceptances can be used to label the nodes of a normalised transition graph, and since $\minaccs(P/s) = \minaccs(G(P)/s)$, the notation of minimal hitting sets also
carries over to graphs: we write $\minhits(n)$ for nodes $n$ of $G(P)$ and observe that
\begin{equation}
\label{eq:minhitsGP}
\minhits(G(P)/s) = \minhits(P/s) \ \text{for all}\ s\in \trc(P).
\end{equation}

% =========================================================================
\subsection{Sperner Families}
\label{sec:sperner}
In preparation of complexity results to be presented in Section~\ref{sec:complexity}, we consider the question how many minimal hitting sets can maximally exist for a given 
collection of minimal acceptances. 
To this end, the following definitions and results are 
useful\footnote{The authors are grateful to Li-Da Tong from National Sun Yat-sen University, Taiwan, 
for suggesting the applicability of Sperner's Theorem in the context of the work presented here.}.

A \emph{Sperner Family} is a collection $S \subseteq 2^\Sigma$ of sets from a given 
finite universe $\Sigma$ that do not contain each other, that is, 
$H_1 \not\subseteq H_2 \wedge H_2 \not\subseteq H_1$ holds for each pair $H_1\neq H_2\in S$. 
Specialising   antichains known from   partial orders to finite sets partially ordered by $\subseteq$ results in Sperner families. 
We observe that
\begin{itemize}
\item the maximal refusals of a CSP process state,
\item the minimal acceptances of a CSP process state, and
\item the minimal hitting sets of a given collection of sets
\end{itemize}
represent Sperner families. Moreover, given any finite alphabet $\Sigma$ with
$\card{\Sigma} = n$, every collection $S$ of subsets with identical cardinality $k \le n$
is a Sperner family,  because $A_1, A_2\in S \wedge A_1 \subseteq A_2\wedge \card{A_1} = \card{A_2}$ implies $A_1 = A_2$. Given  any Sperner Family $S$ of $\Sigma$, $S$ represents
the minimal acceptances in the initial state of the CSP process  
\[
P = \Intchoice_{A\in S}\big( e:A \then P(e) \big).
\]

The cardinality of Sperner Families is determined by the following theorem.
\begin{theorem}[Sperner's Theorem~\cite{sperner_satz_1928}]
\label{th:sperner}
Given a  Sperner family $S$ 
over an $n$-element universe $\Sigma$, its cardinality is bound by
\[
\card{S} \le \binom{n}{\lfloor\frac{n}{2}\rfloor}.
\]
The upper bound is reached if and only if one of the following cases apply.
\begin{enumerate}
\item For even $n$, if $S$ consists of all subsets of $\Sigma$ with cardinality $n/2$.
\item For odd $n$, if one of the following cases holds.
\begin{enumerate}
\item $S$ consists of all subsets of $\Sigma$ with cardinality $(n+1)/s$.
\item $S$ consists of all subsets of $\Sigma$ with cardinality $(n-1)/s$.
\end{enumerate}
\end{enumerate}
\xbox
\end{theorem}
It will be shown in Section~\ref{sec:complexity} that this upper bound can actually be reached by hitting sets associated with the minimal acceptances of a CSP process state.
